Field-informed Reinforcement Learning for Learning Large-Scale Collective Tasks

### 2023-05-11 paper.tex
chore: reduce the image size for the high level description of field-infor rl
typo

\begin{figure*}

@@

\end{figure*}
In this section, we aim to clarify the components involved in our proposed solution (i.e., architecture), how these components interact with each other to bring the system to perform the collective behavior (i.e dynamics), and finally, we will detail the learning algorithm designed and used to synthesise the policy (learning algorithm).

>>>>

\begin{figure}

@@

\end{figure}
In this section, we aim to clarify the components involved in our proposed solution (i.e., architecture), how these components interact with each other to bring the system to perform the collective behaviour (i.e dynamics), and finally, we will detail the learning algorithm designed and used to synthesise the policy (learning algorithm).
